Research Notes

### 2019-02-25 writeups/notes.tex
stash

>>>>

\subsection{Energy Dissipation Thickness}

The wave action $I = \frac{E}{\tilde{\omega}} = \frac{E}{\omega_0 -
k_x\bar{U}_0}$ is a conserved quantity for an adiabatically varying shear flow
$\bar{U}_0(z)$. Then, writing $E = I\tilde{\omega}$, we can compute the energy
dissipation as a function of $z$:
\begin{align*}
    \pd{E}{z} &= -Ik_x\pd{\bar{U}_0}{z},\\
        &= -\frac{E_0}{\omega_0} k_x \pd{\bar{U}_0}{z},\\
        &= -\frac{E_0}{N} \abs*{\vec{k}_0} \pd{\bar{U}_0}{z},\\
        &= -E_0 \frac{\abs*{\vec{k}_0}}{\sqrt{\mathrm{Ri}}}.
\end{align*}

In most astrophysical applications, $k_z \gg k_x$, and so we find that the
characteristic dissipation lengthscale is $\sim
\frac{\sqrt{\mathrm{Ri}}}{k_{z0}}$.
